Crystal as a thermodynamic computer

### 2024-09-05 paper/main.tex
update numerical result parts

\begin{equation}
    t_{total} = \frac{T}{W}(\ln(\frac{T}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

@@

\begin{equation}
P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
\end{equation}

@@

Let us define a model Hamiltonian on a 2D lattice of size $S \times T$ as
\begin{equation}\label{eq:toy-hamiltonian}
H = \sum_{t=1}^{T-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
\end{equation}
where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
Its ground state with energy $0$ encodes a $110$ CA, where the direction of computation is from the left to right.
\subsection{Numerical result}

\ym{I will move this figure to AppendixB to show the equivalent 
between heat bath and energy gradient. Another plot would be put here that
show the TL v.s. $m\ln^{1+\frac{1}{c\ln(\Lambda)}}m$}
We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition
$\Lambda = 1.3, n = 15$ , and fitted each sweep time against
$m \log^2(m)$. Where $m$ represents the number of the single layers,
$n$ represents the width per single layer.

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/numercial result.pdf}
    \caption{Time v.s. Depth of the material}
\end{figure}

Another numerical experiment are conducted to determine the time complexity of the computation along the input memory direction.

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
    \caption{Time v.s. width of the material}
\end{figure}

This indeed informs that the time scale along the memory direction is linear.

>>>>

\begin{equation}
    \label{eq:total-annealing-time}
    t_{total} = \frac{T}{W}(\ln(\frac{T}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

@@

\begin{equation}
    \label{eq:non-equilibrium-SA}
P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
\end{equation}

@@

Denote $S$ to be the length of the material along the ``Space'' axis, $T$
to be the length of the material along the ``Time'' axis. 
Let us define a simpler but equivalent energy model on a 2D lattice of size $S \times T$, whose hamiltonian
is given by
\begin{equation}\label{eq:toy-hamiltonian}
H = \sum_{t=1}^{T-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
\end{equation}

where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
Its ground state with energy $0$ also encodes a $110$ CA, where the direction of computation is from the left to right.
\subsection{Numerical result}

Here we conducted numerical experiments to examine both the time complexity along the ``Space'' direction and the ``Time'' direction.
We use binary search to determine the speed of the slowly moving heat bath at which
the simulated annealing procedure would produce 
a ground state configuration with $50\%$ probability. Denote this speed 
as $v$, the simulated annealing procedure will then take $\frac{T}{v}$
stages to complete the computation, each stage we try to flip a spin with 
probability define in (\ref{eq:non-equilibrium-SA}). We name $\frac{T}{v}$ 
as Sweep Time.

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/MainNumericalResult.png}
    \caption{Numerical Result}
    \label{fig:main-numerical-result}
\end{figure}

[Fig. \ref{fig:main-numerical-result}(a)] shows the relationship between
$\ln(\ln(T))$ and $\ln(\frac{\text{Sweep Time}}{T})$ shoule be linear, which implies 
the time complexity along the ``Time'' direction should scale as $T\ln(T)^{f(\Lambda)}$. 
We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
empirical constant $c$ in (\ref{eq:total-annealing-time}) to be $3$. [Fig. \ref{fig:main-numerical-result}(b)] shows 
the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
we can conclude that the time complexity should scales as $TS\log(T)^{1+\frac{1}{3\ln(\Lambda)}}$, 
which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).
% \begin{figure}[h]
%     \centering
%     \begin{minipage}[b]{0.485\columnwidth}
%         \centering
%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/TimeComplexityalongTaxis.png}
%         \caption{Time v.s. Depth of the material}
%         \label{fig:image1}
%     \end{minipage}
%     \hspace{0.001\columnwidth} % 两张图片之间的水平间距
%     \begin{minipage}[b]{0.485\columnwidth}
%         \centering
%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
%         \caption{Time v.s. width of the material}
%         \label{fig:image2}
%     \end{minipage}
% \end{figure}
